---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ReLTER

<!-- badges: start -->
<!-- badges: end -->

Nell'ambito della rete eLTER

## Installation

You can install the development version of ReLTER from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("oggioniale/ReLTER")
```
## Examples

An examples of the possible capabilities of this library is given below. In these examples you can see interaction, througth API, with DEIMS-SDR.

First example creates a map overlaying the boundaries of the site (Lake Maggiore) thanks to the information on geographical aspects provided by DEIMS-SDR. by function getSiteBoundaries.

```{r, echo = FALSE, message = FALSE, warning = FALSE, results = FALSE, exampleSiteBoundaries}
library(dplyr)
ReLTER::getSiteBoundaries(deimsid = 'https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe')
```


Second example creates a list of parameters collected by a network (LTER-Italy) information always gathered from what is indicated in the different sites on DEIMS-SDR. by function getNetworkParameters

```{r, echo = FALSE, message = FALSE, warning = FALSE, exampleSiteParameters}
library(dplyr)
listParams <- ReLTER::getNetworkParameters(networkDEIMSID = 'https://deims.org/network/7fef6b73-e5cb-4cd2-b438-ed32eb1504b3')
knitr::kable(listParams[1:10, ])
```