---
title: "ReLTER"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ReLTER}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.ext = 'png',
  out.width = "100%"
)
```

## Description of <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span>
<span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span> is an R package that: provides access to [DEIMS-SDR](https://deims.org/)), allows interact with software implemented by eLTER Research Infrastructure (RI) and improves the data/information shared by them.
<span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span> is a R package devoted to access, interact and improve the information and the data shared by Long Term Ecological Research (LTER) network. This package is born within eLTER H2020 major project that will help advance the development of European Long-Term Ecosystem Research Infrastructures ([eLTER RI](https://elter-ri.eu)).

The <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span> package functions in particular allow to:

- retrive the information about entities (e.g. sites, datasets, and activities) shared by [DEIMS-SDR](https://deims.org/) (see e.g. [get_site_info function](https://oggioniale.github.io/ReLTER/reference/get_site_info.html));

- elaborate the information of single site or merge info from national network sites or entire International LTER (ILTER) in order to provide maps, figures, graphs etc (see e.g. [get_network_sites](https://oggioniale.github.io/ReLTER/reference/get_network_sites.html), [produce_site_map](https://oggioniale.github.io/ReLTER/reference/produce_site_map.html) or [produce_site_parameters_pie](https://oggioniale.github.io/ReLTER/reference/produce_site_parameters_pie.html) functions);

- interact with the [ODSEurope](maps.opendatascience.eu) managed by members of the [Geo-harmonizer](https://opendatascience.eu/geoharmonizer-project/) project starting with the dataset shared by [DEIMS-SDR](https://deims.org/) (see e.g. [get_site_ODS](https://oggioniale.github.io/ReLTER/reference/get_site_ODS.html) function);

- improve the quality of the dataset (see e.g. [get_id_worms](https://oggioniale.github.io/ReLTER/reference/get_id_worms.html)).

Functions currently implemented are derived from the discussion of the needs declared by eLTER users community.

The <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span> package shall definitely follow the progress of eLTER-RI infrastructure and evolving with the improvements and develop of new tools.

## Citation of <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span>

To cite <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span> please use:
Alessandro Oggioni, Micha Silver & Paolo Tagliolato. (2021). oggioniale/ReLTER: ReLTER v1.0.0 (1.0.0). Zenodo. https://doi.org/10.5281/zenodo.5576813

or:

``` bibtex
@software{alessandro_oggioni_2021_5576813,
  author       = {Alessandro Oggioni and Micha Silver and Paolo Tagliolato},
  title        = {oggioniale/ReLTER: ReLTER v1.0.0},
  month        = nov,
  year         = 2021,
  publisher    = {Zenodo},
  version      = {1.0.0},
  doi          = {10.5281/zenodo.5576813},
  url          = {https://doi.org/10.5281/zenodo.5576813}
}
```

## Documentation of <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span>

You can visit <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span> website at [oggioniale.github.io/ReLTER/](https://oggioniale.github.io/ReLTER/) for obtain documentation on installation, functions description and examples of use.


## Installation of <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span>

You can install the development version of <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span> from [GitHub](https://github.com/oggioniale/ReLTER) with:

```{r, installationInfo, eval = FALSE}
install.packages("devtools")
devtools::install_github("oggioniale/ReLTER")
```


## Code of Conduct of <span style="color:#2878B3;font-size:90%;font-weight:normal;">ReLTER</span>

Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
