---
title: "How to get the info of a (one) LTER Site by knowing the DEIMS.ID"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to get the info of a (one) LTER Site by knowing the DEIMS.ID}
  %\VignetteEngine{knitr::knitr}
  %\usepackage[UTF-8]{inputenc}
  bibliography: ./references/occurrences_into_site_refs.bib
author: "Alessandro Oggioni, Paolo Tagliolato"
---

For each LTER site the information are provided, by site manager, into DEIMS-SDR registry (see <https://deims.org>). The LTER site's information are grouped into main sections, the most important ones are:

* Affiliations,
* Boundaries,
* Contacts,
* Environmental characteristics,
* General,
* Infrastructure,
* Parameters,
* Relate resources.

For more details about the site data model please visit <https://deims.org/models/?id=site>.

The [`get_site_info`](https://docs.ropensci.org/ReLTER/reference/get_site_info.html) function of {ReLTER} allows to download details about a specific site, through the DEIMS-SDR sites API and the DEIMS.ID (<https://deims.org/docs/deimsid.html>).

## Get affiliation info of the LTER site:

If the aim is to obtain the info about in which networks/RIs the site is listed, you can: 

```{r aff, warning=FALSE}
siteAffiliations <- ReLTER::get_site_info(
  deimsid = 'https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe',
  categories = 'Affiliations'
)
# network(s) where the site is involved in
knitr::kable(
  siteAffiliations$data$networks[[1]],
  caption = "The list of the network(s) in which the site is listed"
)
# project(s) where the site is involved in
knitr::kable(
  siteAffiliations$data$projects[[1]],
  caption = "The list of the project(s) in which the site is listed"
)
```

## Get boundaries info of the LTER site:

If the aim is to obtain the info about the geographic extent covering the area of all measurements, you can: 

```{r bound, warning=FALSE}
siteInfo <- ReLTER::get_site_info(
  deimsid = "https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe",
  show_map = TRUE
)
```

## Get Contacts info of the LTER site:

If the aim is to obtain the info about the reference to the contact person responsible for the site, the organisation operating the site and its monitoring programme(s), the reference to the organisation or the responsible national authority for funding and strategic decisions about the site or the full name of the person(s) or organisation(s) who created the documentation for the site, you can: 

```{r contacts, warning=FALSE}
siteContact <- ReLTER::get_site_info(
  deimsid = "https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe",
  categories = "Contacts"
)
# site manager(s)
knitr::kable(
  siteContact$data$siteManager[[1]],
  caption = "The list of the manager(s) of site"
)
# operating organisation of site
knitr::kable(
  siteContact$data$operatingOrganisation[[1]],
  caption = "The list of the operating organization of the site"
)
# metadata provider(s) of site
knitr::kable(
  siteContact$data$metadataProvider[[1]],
  caption = "The list of the metadata provider(s) of site"
)
# funding agency(ies) of site
knitr::kable(
  siteContact$data$fundingAgency[[1]],
  caption = "The list of the funding agency(ies) of site"
)
```

The same approach could be used for other category information.

```{r otherInfo}
siteGeneral <- ReLTER::get_site_info(
  deimsid = "https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe",
  categories = "General"
)
siteGeneral$data
siteInfrastructure <- ReLTER::get_site_info(
  deimsid = "https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe",
  categories = "Infrastructure"
)
siteInfrastructure$data$collection[[1]]
siteEnvCharacts <- ReLTER::get_site_info(
  deimsid = "https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe",
  categories = "EnvCharacts"
)
siteEnvCharacts$data
```

By selecting the category Infrastructure you can obtain info as:

* access type
* data policy

By selecting the category Infrastructure you can obtain info as:

* air temperature (min, max and average)
* precipitation (min, max and average)
* biogeographical region
* biome
* ecosystem type
* eunis habitat
* geoBon biome
* geology
* hydrology
* soil
* vegetation

## Get list of parameters or related resources declared to the LTER site:

```{r listInfo}
siteObsProp <- ReLTER::get_site_info(
  deimsid = "https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe",
  categories = "observedProperties"
)
# parameter(s) collected in the site
knitr::kable(
  siteObsProp$data$observedProperties[[1]],
  caption = "The list of the funding agency(ies) of site"
)

siteRelateRes <- ReLTER::get_site_info(
  deimsid = "https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe",
  categories = "RelateRes"
)
# resource(s) related to the site (e.g. datasets, activities)
knitr::kable(
  siteRelateRes$data$relatedResources[[1]],
  caption = "The list of the funding agency(ies) of site"
)
```

Finally if you want get info from multiple site, please visit [this page](./sites_information.html).